\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

%SetFonts

%SetFonts


\title{Search strategy  for updating evidence on the duration of untreated chlamydia infections in men}
\author{Joanna Lewis}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle

For our evidence synthesis we used three published literature reviews to identify relevant studies, in which chlamydia-infected men were re-tested at a later date having received no treatment in the interim. Two of the reviews provided information on their search methodology, and we updated these searches to cover the period since the original review. The search strategy for these updates is provided here.

\section{Geisler WM. \textit{J Infect Dis} (2010)}

The more recent review was: Geisler WM. Duration of untreated, uncomplicated Chlamydia trachomatis genital infection and factors associated with chlamydia resolution: a review of human studies. \textit{J Infect Dis} \textbf{201}:S104-S113 (2010).

We searched MEDLINE using the Ovid service on 5 April 2017, using the following queries:

\begin{enumerate}

\item{Chlamydia/}
\item{Chlamydia.ab,ti.}
\item{1 or 2}
\item{exp Natural History/}
\item{untreated.ab,ti.}
\item{spontaneous resolution.ab,ti.}
\item{exp Remission, Spontaneous/}
\item{duration.ab,ti.}
\item{clearance.ab,ti.}
\item{eradication.ab,ti.}
\item{resolved.ab,ti.}
\item{exp Recurrence/}
\item{relapse.ab,ti.}
\item{remission.ab,ti.}
\item{repeat.ab,ti.}
\item{persistence.ab,ti.}
\item{exp Follow-Up Studies/}
\item{subsequent.ab,ti.}
\item{4 or 5 or 6 or 7 or 8 or 9 or 10 or 11 or 12 or 13 or 14 or 15 or 16 or 17 or 18}
\item{3 and 19}
\item{limit 20 to (english language and humans and yr ``2008-Current'' and (``all adult (19 plus years)'' or ``adolescent (13 to 18 years)'' or ``young adult (19 to 24 years)'' or ``adult (19 to 44 years)'' or ``young adult and adult (19-24 and 19-44)'' or ``middle age (45 to 64 years)'' or ``middle aged (45 plus years)'' or ``all aged (65 and over)'' or ``aged (80 and over)''))}

\end{enumerate}

The final search (number 21) returned 415 results.

\section{Golden MR \textit{et al. Sex Transm Dis} (2000)}

An older review was: Golden MR, Schillinger JA, Markowitz L and St Louis ME. Duration of untreated genital infections with Chlamydia trachomatis: A review of the literature. \textit{Sex Transm Dis} \textbf{27}:329-337 (2000)

We searched MEDLINE using the Ovid service on 5 April 2017, using the following queries:

\begin{enumerate}

\item{exp Chlamydia/}
\item{exp Chlamydia Infections/}
\item{Chlamydia.mp. [mp=title, abstract, original title, name of substance word, subject heading word, keyword heading word, protocol supplementary concept word, rare disease supplementary concept word, unique identifier, synonyms]}
\item{1 or 2 or 3}
\item{exp Remission, Spontaneous/}
\item{exp Follow-Up Studies/}
\item{exp time/ or exp time factors/}
\item{exp Randomized Controlled Trials as Topic/}
\item{resolution.mp. [mp=title, abstract, original title, name of substance word, subject heading word, keyword heading word, protocol supplementary concept word, rare disease supplementary concept word, unique identifier, synonyms]}
\item{follow-up.mp. [mp=title, abstract, original title, name of substance word, subject heading word, keyword heading word, protocol supplementary concept word, rare disease supplementary concept word, unique identifier, synonyms]}
\item{5 or 6 or 7 or 8 or 9 or 10}
\item{4 and 11}
\item{limit 12 to yr=``1996-Current''}

\end{enumerate}

The final search (number 13) returned 1874 results.

\end{document}  